Analysis_v1.1_weather

### 2022-03-15 R/Analysis_v1.1_weather_2020.Rmd
Add phenotypic covariance matrices for 8 sites for 2019 phenology data

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(here)
library(zoo)
library(lubridate)
library(cowplot)
```

@@

>>>>

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(here)
library(zoo)
library(lubridate)
library(cowplot)
library(rlist)
```

@@

# P covar for Li

```{r}
metadata <- read_rds(here("data", "metadata.rds"))
subpop_v2 <- list(Gulf_and_Midwest = c("Gulf", "Midwest"), Midwest = "Midwest",
                  Gulf = "Gulf")
year_v = c(2019, 2020, 2021)
gr_ten_sites <- readRDS(file = here("data",
                                    "Weather_related_phe_GR50_3yr.rds"))
fl_ten_sites <- readRDS(here("data", "Weather_related_phe_FL50_3yr.rds"))

    cov_df <- fl_ten_sites %>%
      ungroup() %>%
      filter(SUBPOP %in% subpop_v2[[k]]) %>%
      filter(Year %in% 2019) %>%
      select(PLANT_ID, SUBPOP, manu_site, phe_hyp[i]) %>%
      group_by(PLANT_ID, SUBPOP, manu_site) %>%
      mutate(IND = row_number()) %>%
      pivot_wider(names_from = manu_site, values_from = phe_hyp[i]) %>%
      mutate(PLANT_ID = as.factor(PLANT_ID),
             IND = as.factor(IND)) %>%
      select(PLANT_ID, SUBPOP, IND, MI, MO, NE, OK, SD, TX1, TX2, TX3) #####

    cor_phe <- cor(cov_df[,-(1:3)], use = "pairwise")
    # Set diagonal of this matrix = coefficient of variation within each garden.
    diag(cor_phe) <- cov_df %>%
      ungroup() %>%
      summarise(MI = sqrt(var(MI, na.rm = TRUE))/mean(MI, na.rm = TRUE),  #####
                MO = sqrt(var(MO, na.rm = TRUE))/mean(MO, na.rm = TRUE),
                NE = sqrt(var(NE, na.rm = TRUE))/mean(NE, na.rm = TRUE),
                OK = sqrt(var(OK, na.rm = TRUE))/mean(OK, na.rm = TRUE),  #####
                SD = sqrt(var(SD, na.rm = TRUE))/mean(SD, na.rm = TRUE),
                TX1 = sqrt(var(TX1, na.rm = TRUE))/mean(TX1, na.rm = TRUE),
                TX2 = sqrt(var(TX2, na.rm = TRUE))/mean(TX2, na.rm = TRUE),
                TX3 = sqrt(var(TX3, na.rm = TRUE))/mean(TX3, na.rm = TRUE)) %>%
      as_vector()

phe_hyp <- c("cgdd_12c_10d", "cgdd_12c_20d", "cgdd_12c_5d", 
             "tave_5d", "tave_10d", "tave_20d")

U_hyp_2019_gr <- list()
for(i in seq_along(phe_hyp)){
  for(k in seq_along(subpop_v2)){

    cov_df <- gr_ten_sites %>%
      ungroup() %>%
      filter(SUBPOP %in% subpop_v2[[k]]) %>%
      filter(Year %in% 2019) %>%
      select(PLANT_ID, SUBPOP, manu_site, phe_hyp[i]) %>%
      group_by(PLANT_ID, SUBPOP, manu_site) %>%
      mutate(IND = row_number()) %>%
      pivot_wider(names_from = manu_site, values_from = phe_hyp[i]) %>%
      mutate(PLANT_ID = as.factor(PLANT_ID),
             IND = as.factor(IND)) %>%
      select(PLANT_ID, SUBPOP, IND, MI, MO, NE, OK, SD, TX1, TX2, TX3) #####

    cor_phe <- cor(cov_df[,-(1:3)], use = "pairwise")
    # Set diagonal of this matrix = coefficient of variation within each garden.
    diag(cor_phe) <- cov_df %>%
      ungroup() %>%
      summarise(MI = sqrt(var(MI, na.rm = TRUE))/mean(MI, na.rm = TRUE),  #####
                MO = sqrt(var(MO, na.rm = TRUE))/mean(MO, na.rm = TRUE),
                NE = sqrt(var(NE, na.rm = TRUE))/mean(NE, na.rm = TRUE),
                OK = sqrt(var(OK, na.rm = TRUE))/mean(OK, na.rm = TRUE),  #####
                SD = sqrt(var(SD, na.rm = TRUE))/mean(SD, na.rm = TRUE),
                TX1 = sqrt(var(TX1, na.rm = TRUE))/mean(TX1, na.rm = TRUE),
                TX2 = sqrt(var(TX2, na.rm = TRUE))/mean(TX2, na.rm = TRUE),
                TX3 = sqrt(var(TX3, na.rm = TRUE))/mean(TX3, na.rm = TRUE)) %>%
      as_vector()

    U_hyp_2019_gr <- list.prepend(U_hyp_2019_gr, cor_phe)
    names(U_hyp_2019_gr)[1] <- paste0(phe_hyp[i], "_", names(subpop_v2)[k])
  }
}

saveRDS(U_hyp_2019, file = here("data", "P_covar_matrices_flowering_2019_8sites.rds"))
saveRDS(U_hyp_2019_gr, file = here("data", "P_covar_matrices_greenup_2019_8sites.rds"))
```
